Measurement of a dwarf galaxy rotational velocity from its Lyman-alpha line emission

### 2016-06-19 paper/letter.tex
Added paragraphs about multiphase-model.

>>>>

The idealized multiphase model consists of spherical, cold, dens clumps of neutral hydrogen (and dust) embedded in a hot, ionized medium. The clumps also have a random and an outflowing velocity component which totals the number of parameters describing the model to be $14$. In order to map out this large parameter space, we randomly drew $2500$ sets of parameters within a observationally realistic range (based on the considerations of \cite{Laursen2013ApJ...766..124L}) yielding a large variety of single-, double- and triple-peaked spectra. The full analysis of the the spectral features as well as more details on the radiative transfer are presented in \cite{Gronke2016}.

\textbf{MG: I don't know how much details you want -- should we name all of the $14$ (best fit) parameters? Just delete what is unnecessary.}

For the current work, we computed the $\chi^2$ for each of the $2500$ parameters yielding the best fit parameters of $(...)$. Here, the subscripts ${}_{\rm cl}$ and $_{\rm ICM}$ stand for the quantities filling the clumps and the medium between the clumps, respectively. Furthermore, we found that some parameters such as the magnitude of the random clump motion $\sigma_{\rm cl}$ improved the fit significantly whereas others did not. This makes sense also qualitatively as \tol\ possesses a very wide spectrum which can be achieved by subsequent scatterings off (relatively) fast moving clumps while the multi-phase nature (i.e., the existence of low-density channels) ensures the high flux at line center as observed.
